Refinements for Open Automata

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
Red arrow for open transition
Deadlock reduction parenthesis
More todos

% symbolic
Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}. Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system. In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the input values. This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states of two systems but it is additionally  parameterised by a formula that must be verified by the state variables. This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.

>>>>

% symbolic
Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}. Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system. In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the input values. This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states of two systems but it is additionally  parameterised by a formula that must be verified by the state variables. This has been introduced in details in previous works~\cite{AMHEEMA:2023} and will be recalled briefly in Section~\ref{sec:def}. We have shown in previous works that open symbolic systems are particularly convenient to model process algebra operators and open component systems with infinite behaviour~\cite{AMHEEMA:2023,henrio:01299562}.
